\subsection{Differential expression analysis}
Differential expression quantifiers including log2 fold change and FDR  were computed using the R 3.6.0 Bioconductor package \texttt{edgeR\_3.26.0} that implements scRNAseq differential expression analysis methodology based on the negative binomial distribution. Given the raw counts for the cells in two clones, we first call the \texttt{estimateDisp()} function to estimate the dispersion by fitting a generalized linear model that accounts for all systematic sources of variation. Next, we use the \texttt{edgeR} functions \texttt{glmQLFit()} and \texttt{glmQLFTest()} to perform a quasi-likelihood dispersion estimation and hypothesis testing that assigns false discovery rate values to each gene. In the track and volcano plots, a positive log2 fold change value for clone X relative to clone Y signifies that the gene is significantly more upregulated (at a given FDR threshold) in X than in Y while taking into consideration all the expression values for all the genes in both clones. Similarly, a gene with negative log2 fold change is significantly more downregulated in X than in Y.

\subsection{Global proportion figure figure2}

Panel A: 
Proportion in genome: we do \texttt{sitka} tree inference, then we can group cells with similar profiles into clones. So for each clone, we summary each clone by its median copy number profile. 
median copy number profile : for each segment position, we get copy number state of each cell in this clone, and get median of copy number state. 

In total, we have 9000 segment position with copy number change out of 22k positions. 
We do intersection with DE genes that we obtained from DE analysis using edgeR, see that there are 2000 segment position that have copy number -genes driven. 
2000/9000 --> red color (they are matching with our DE genes)
7000/9000 --> green colors with copy number change. Genes in transcriptome can have drug effect but not significant difference between 2 clones in rna-seq DE analysis. 


Panel B: edgeR
Do differential expression resistant vs sensitive (EdgeR), 
we found . 4000 DE genes
We find overlap between these DE genes with segment copy number position. 
Ex: 2000 incis, 2000/4000 = 50\% in cis , divide into increase and decrease
2000 in-trans, divide into up-regulated and down-regulated 

\subsection{Line trajectories-Fig3}
- From Hoas volcanoes DE common genes





\subsection{Volcanoes and track plots}






\subsection{Pathways evolution}




\subsection{Regression analysis}




\subsection{Line trajectories-From the regression out put and pathways}
did you select common genes in all PDX? or did you select from sensitive to resistant?
